One more attempt on ArXe

### 2016-05-25 intro.tex

A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{Fasshauer10} and the seondary electron spectra were simulated for
model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
for combinations of argon and xenon atoms with larger interatomic distances. 
Again, we will detail these results in conjunction with our 
current work.

>>>>

A number of theoretical works on Ar-Xe clusters aimed at the prediction of minimum energy structures. 
Most recently, these converged to structures which have the Xe atoms mainly in the interior.\cite{marques} 
Xe was also found to diffuse into the interior of Ar clusters in molecular dynamics simulations after pick-up.\cite{Vach_1999} 
The electronic energy levels of very small Ar-Xe clusters were calculated in Ref.~ \citenum{fasshauer} and the seondary electron spectra were simulated for
model structures of one argon atom placed on a xenon surface \cite{Fasshauer13}.
Interestingly, it was found that Ar 3s$^{-1}$ is stable 
against autoionization in an ArXe dimer, but is destabilized by 
adding further Xe atoms, or an Ar solvation shell, to the system, thereby allowing
for combinations of argon and xenon atoms with larger interatomic distances. 
Again, we will detail these results in conjunction with our 
current work.

### 2016-05-25 summary.tex

\section{Summary}
%
In summary, we have presented comprehensive experimental and theoretical data for the autoionization of inner valence ionized states in ArXe clusters.
Both ICD and ETMD are allowed for most cases we considered.
Because of energetical reasons ICD requires a separation of the final state vacancies by about 8~\AA or more, which is at least two times the typical Ar-Xe distance.
We found that autoionization has 0.8 to 1.0 efficiency within the experimental accuracy, that is it dominates over other modes of relaxation.
By comparing our measured spectra to calculations, we identified `long range' ICD as the most important decay mode.

>>>>

\section{Summary}
%
We have presented comprehensive experimental and theoretical data for the
autoionization of inner valence ionized states in ArXe clusters.
Both ICD and ETMD are allowed for most cases we considered.
Because of energetical reasons ICD requires a separation of the final state
vacancies of \unit[7.58]{\AA} or more, which is about two times the typical
Ar-Xe distance.
We found that autoionization has an efficiency of 0.8 to 1.0 within the
experimental accuracy, that is it dominates over other modes of relaxation.
By comparing our measured spectra to calculations, we identified `long range'
ICD as the most important decay mode.
